On The Impact of Atoms of Confusion in JavaScriptCode

### 2022-07-27 3_Method.tex
First feature-complete version of the paper. It is enormous.

\begin{enumerate}[(RQ1)]
\item \rqa 
\item \rqb
% \item \rqc  
\item \rqd\castor{This one will probably be removed.}
\end{enumerate}

By answering these research questions, we can either generalize or refute the findings about atoms of confusion already discussed in the literature (goal of research questions (RQ1) and (RQ2)). 
\castor{The following pertains to the third RQ.}
In addition, answering the third question allows us to enrich existing catalogs about atoms of confusion and discuss how often they occur in practice\castor{This should probably be removed.}. Answering these research questions also lays the foundations for the implementation of tools that can automatically transform code into cleaner versions.
%---though we postpone these results to future research work.
We conduct a mixed-methods study to answer these questions. 
It includes two independently designed and conducted experiments: a repeated measures/within subjects study and one using a Latin square, counterbalancing experimental design to control for subject experience. By using two different experiments, designed by different researchers, with different designs, and conducted with different participants, we hope to rigorously verify the impact of atoms of confusion in code comprehension activities. These two experiments explore the impact of atom candidates on understanding JavaScript code (goal of research question RQ1). They investigate whether or not programs that contain atom candidates tend to produce more misunderstanding for programmers trying to predict their outcome.% We leverage two independently-developed and conducted experiments with different designs to more  
We also conduct a set of interviews with developers to contrast the quantitative results of the experiments with their preferences and opinions (thus addressing RQ2).

@@

\castor{We must have introduced the atoms before.}
The first experiment we perform uses a repeated measures, or within-subject, design~\cite{Keselman:2001:ARM}. This experiment is inspired by the work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}, but targeting JavaScript instead of the C language, and including some methodological differences. It covers all the atom candidates analyzed in the work of Gopstein et al. that can be transposed to JavaScript and adds candidates that are specific to this language.
%Overall, we select 24 atom candidates in the repeated measures study.

@@

\subsection{Interview Study Setting}

@@

\subsection{Mining JavaScript Software Repositories Setting}

>>>>

\begin{enumerate}[(RQ1)]
\item \rqa 
\item \rqb
% \item \rqc  
\item \rqd
\end{enumerate}

By answering these research questions, we can either generalize or refute the findings about atoms of confusion already discussed in the literature (goal of research questions (RQ1) and (RQ2)). 
In addition, answering the third question allows us to enrich existing catalogs about atoms of confusion and discuss how often they occur in practice. Answering these research questions also lays the foundations for the implementation of tools that can automatically transform code into cleaner versions.
%---though we postpone these results to future research work.
We conduct a mixed-methods study to answer these questions. 
It includes two independently designed and conducted experiments: a repeated measures/within subjects study (Section~\ref{sec:meth:replication}) and one using a Latin square, counterbalancing experimental design to control for subject experience (Section~\ref{sec:meth:survey}). By using two different experiments, designed by different researchers, with different designs, and conducted with different participants, we hope to rigorously verify the impact of atoms of confusion in code comprehension activities. These two experiments explore the impact of atom candidates on understanding JavaScript code (goal of research question RQ1). They investigate whether or not programs that contain atom candidates tend to produce more misunderstanding for programmers trying to predict their outcome.% We leverage two independently-developed and conducted experiments with different designs to more  
We also conduct a set of interviews with developers (Section~\ref{sec:method:interview}) to contrast the quantitative results of the experiments with their preferences and opinions (thus addressing RQ2). Finally, we perform a repository mining study (Section~\ref{sec:method:msr}) that investigates the prevalence of some of these atom candidates in large scale, professionally-developed JavaScript software.

@@

The first experiment we perform uses a repeated measures, or within-subject, design~\cite{Keselman:2001:ARM}. This experiment is inspired by the work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}, but targeting JavaScript instead of the C language, and including some methodological differences. It covers all the atom candidates analyzed in the work of Gopstein et al. that can be transposed to JavaScript and adds candidates that are specific to this language.
%Overall, we select 24 atom candidates in the repeated measures study.

@@

\subsection{Interview Study Setting}\label{sec:method:interview}

@@

\subsection{Mining JavaScript Software Repositories Setting}\label{sec:method:msr}

### 2022-07-27 4_Result.tex
First feature-complete version of the paper. It is enormous.

\begin{table}[t!]
\caption{Summary of the correctness analysis.}
\label{tab:diff-correctness-repeated}
\centering{
  \begin{scriptsize}
\begin{tabular}{lccc} \toprule
  Atom & Obfuscated & Clean & $\Delta$(\%)  \\ \midrule
Type Conversion           &            5 &      27 &                 +440 \\
Change of Literal Encoding &           9 &      36 &                 +300 \\
Comma Operator            &            8 &      29 &                 +262 \\
Object Destructuring      &           15 &      42 &                 +180 \\
Assignment As Value       &           18 &      43 &                 +139 \\
Pre-Increment             &           13 &      28 &                 +115 \\
Post-Increment            &            8 &      17 &                 +112 \\
Array Destructuring       &           15 &      28 &                 +87 \\
Indentation no Braces     &           30 &      50 &                 +67 \\
Omitted Curly Braces      &           35 &      51 &                 +46 \\
Object Spread             &           21 &      30 &                 +43 \\
Array Spread              &           22 &      31 &                 +41 \\
Automatic Semicolon Insertion &       15 &      21 &                 +40 \\
Infix Operator Precedence &           47 &      53 &                 +13 \\
Arrow Function            &           54 &      58 &                  +7 \\
Implicit Predicate        &           41 &      44 &                  +7 \\
Indentation With Braces   &           53 &      55 &                  +4 \\
Conditional Operator      &           60 &      62 &                  +3 \\
Constant Variables        &           59 &      61 &                  +3 \\
Dead Unreachable Repeated &           63 &      64 &                  +2 \\
Repurposed Variables      &           23 &      23 &                   0 \\
Arithmetic as Logic       &           52 &      47 &                 -10 \\
Logic as Control Flow     &           33 &      28 &                 -15 \\
Property Access           &           51 &      42 &                 -18 \\
\bottomrule  
\end{tabular}
\end{scriptsize}
}
\end{table}

@@

The ``McNemar test'' column of Table~\ref{tab:repeated:misunderstanding} indicates the p-values for the tests. These p-values are compared against an alpha of 0.0021, after applying Bonferroni correction (0.05/24). One of the atom candidates, Constant Variables, is omitted from the table because, due to the very low number of mistakes, it is not possible to perform the test. The table shows that eight of the 24 analyzed atom candidates can be considered atoms of confusion based on the results of our study, Object Destructuring, Type Conversion, Change of Literal Encoding, Comma Operator, Indentation No Braces, Assignment as Value, Pre-Increment, and Ommitted Curly Braces. Among these eight, only Object Destructuring is JavaScript-specific. Six of the other atoms have been previously reported for the C language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} and five for Java~\cite{Langhout:2021:ACJ}. Indentation No Braces is not specific to JavaScript, but has not been studied previously. For some candidates that have been previously identified as atoms, there was not a statistically significant difference. This is the case for Repurposed Variables, Logic as Control Flow, Implicit Predicate, and Conditional Operator.

@@

\begin{table}[th!]
\caption{Hypotheses Testing (correctness). Asterisks ($^{*}$) indicate a statistically significant difference. Using Bonferroni correction, a p-value is considered statistically significant if it is lower than 0.0021.}
 \centering
 {\scriptsize 
 \begin{tabular}{lrr}
   \toprule
Atom candidate & McNemar test &      odds ratio \\
\midrule
Object Destructuring      &   \textbf{$<$ 0.0001*} & $\infty$ \\
Type Conversion           &   \textbf{$<$ 0.0001*} & 12.0 \\
Change of Literal Encoding   &   \textbf{$<$ 0.0001*} & 28.0 \\
Comma Operator            &   \textbf{$<$ 0.0001*} & 11.5 \\
Indentation No Braces     &   \textbf{$<$ 0.0001*} &  11.0 \\
Assignment As Value       &   \textbf{$<$ 0.0001*} &  9.3 \\
Pre-Increment              &  \textbf{0.0003*} &    16.0 \\
Omitted Curly Braces      &  \textbf{0.0009*} &  6.3 \\
Array Destructuring       &  0.0023 &     7.5 \\
Post-Increment              &  0.0225 &     5.5 \\
Array Spread              &  0.0490 &    3.3 \\
Object Spread             &  0.0636 &     2.8 \\
Property Access           &  0.0636 &     2.8 \\
Infix Operator Precedence &  0.1796 &     2.5 \\
Arrow Function            &  0.2891 &     3.0 \\
Arithmetic As Logic       &  0.3323 &  1.8 \\
Automated Semicolon Insertion  &  0.3915 &  1.4 \\
Logic As Control Flow     &  0.4421 &  1.5 \\
%Constant Variables        &  0.5000 &     0.0 \\
Implicit Predicate        &  0.6900 &  1.3 \\
Indentation With Braces   &  0.7266 &  1.7 \\
Conditional Operator      &  0.7905 &  1.3 \\
Dead Unreachable Repeated &  1.0000 &     1.5 \\
Repurposed Variables      &   1.0000 &     1.0 \\
\bottomrule
\end{tabular}
}
\label{tab:repeated:misunderstanding}
\end{table}

@@

\begin{table}[htbp]
\caption{Summary of the correctness analysis}
\label{tab:difference-correctness}
\centering{
  {\scriptsize
  \begin{scriptsize}
\begin{tabular}{lccc} \toprule
  Atom & Obfuscated & Clean & $\Delta$(\%)  \\ \midrule
  Comma Operator                &  28 &  65 & +132   \\ 
  Automatic Semicolon Insertion &  32 &  68 & +112   \\ 
  Post-Increment                &  48 &  64 & +33    \\ 
  Omitted Curly Braces          &  47 &  58 &  +23   \\
  Assignment as Value           &  56 &  68 &  +21   \\ 
  Implicit Predicate            &  58 &  68 &  +17   \\ 
  Logic as Control Flow         &  41 &  48 &  +17   \\ 
  Conditional Operator              &  60 &  66 &  +10   \\ 
  Pre-Increment                 &  50 &  53 &  +6    \\ 
  Arithmetic as Logic           &  64 &  63 &  -2    \\ \bottomrule

@@

\begin{figure}[b!]
\noindent
 \centering
 \includegraphics[width=\columnwidth]{images/wrong-answers-plot-1.pdf}
 \caption{Number of wrong answers of each subject.}
 \label{fig:boxplotcorrectness}
 \end{figure}% \castor{Fiz de tudo para ajeitar a figura porque o texto embaixo deveria ser "Clean versions" e "Confusing versions" mas não sei porque não funcionou. Até mudei a figura. Não sei o que está havendo.}

@@

Finally, we also use a \emph{Binomial Generalized Logistic Regression} analysis to investigate if either \emph{participant education} or \emph{participant experience} impacts correctness. The findings suggest that \emph{participant experience} impacts the results related to correctness (Figure~\ref{fig:correctness-over-experience}). Even though the presence of atoms of confusion reduces the number of correct answers for all \emph{experience groups}, this effect is not uniform. For instance, novice developers (under one year of experience) provide a higher number of wrong answers for the obfuscated version of the code (57.8\%), while developers with more than four years of experience provide more than 70\% of correct answers even when evaluating the obfuscated version of the code snippets. It is also important to note that, independently of the \emph{experience group}, developers tend to provide more than 84\% of correct answers while predicting the outputs for the clean versions of the code. We replicate the \emph{Pearson's Chi-squared test} for each experience group and find that the statistical difference is less significant for those developers with more than ten years of experience. Differently from \emph{participant experience}, the factor \emph{participant education} does not significantly change the correctness of the answers.
\castor{I'd like to have the numbers for the results above. What are the p-values, regression coefficients, etc.?}
\begin{figure}
  \includegraphics[scale=0.3]{images/correctness-by-experience}
  \caption{Impact of atoms of confusion on the correctness (over the four participant experience groups)}
  \label{fig:correctness-over-experience}
\end{figure}

@@

\begin{table}[htbp]
\caption{Time in seconds to submit a correct answer}
\centering{
  {\scriptsize
  \begin{scriptsize}
\begin{tabular}{lccc} \toprule
Atom & Obfuscated  & Clean & $\Delta$(\%) \\ \midrule
Comma Operator & 87.67 & 20.84 & -76.23 \\ 
Automatic Semicolon Insertion & 46.08 & 22.04 & -52.17 \\ 
Post-Increment & 28.70 & 25.67 & -10.56 \\ 
Omitted Curly Braces & 48.85 & 30.00 & -38.58 \\ 
Assignment as Value & 52.47 & 48.95 & -6.71 \\ 
Implicit Predicate & 36.24 & 24.01 & -33.75 \\ 
Logic as Control Flow & 108.94 & 51.07 & -53.12 \\ 
Conditional Operator & 41.80 & 39.34 & -5.90 \\ 
Pre-Increment & 30.71 & 42.45 & 38.19 \\  
Arithmetic as Logic & 28.82 & 37.20 & 29.06 \\ \bottomrule
\end{tabular}
\label{tab:difference-time-taken}
\end{scriptsize}
}}
\end{table}

 % latex table generated in R 4.0.4 by xtable 1.8-4 package
 % Thu Apr 22 07:58:21 2021
 \begin{table*}[ht]
\caption{Hypotheses Testing (misunderstanding and time). Asterisks ($^{*}$) indicate a statistically significant difference.}
 \centering
 {\scriptsize
 \begin{tabular}{lccc|cc}
   \toprule
Atom  & Chi-square & Odds          & CI & Mann-Whitey& Cliff's\\ 
 &  test &Ratio          & CI &  U test & Delta \\  \midrule
Comma Operator & \textbf{$<$ 0.0001*} & 19.02 & (6.60, 68.22) & \textbf{$<$ 0.0001*} & -0.53 \\ 
Automatic Semicolon Insertion & \textbf{$<$ 0.0001*} & 39.33 & (9.21, 356.62) & 0.0980 & -0.16 \\ 
Post-Increment & \textbf{0.0015*} & 4.83 & (1.73, 15.74) & 0.1201 & 0.15 \\ 
Omitted Curly Braces & 0.0510 & 2.35 & (1.00, 5.77) & 0.9253 & -0.01 \\ 
Assignment as Value & \textbf{0.0035*} & 8.39 & (1.81, 79.12) & 0.8268 & 0.02 \\ 
Implicit Predicate & \textbf{0.0112*} & 6.95 & (1.46, 66.56) & \textbf{0.0029*} & -0.29 \\ 
Logic as Control Flow & 0.2920 & 1.54 & (0.73, 3.28) & \textbf{$<$ 0.0001*} & -0.39 \\ 
Conditional Operator & 0.1590 & 2.73 & (0.74, 12.57) & 0.2407 & -0.12 \\ 
Pre-Increment & 0.7015 & 1.25 & (0.55, 2.85) & \textbf{0.0062*} & 0.27 \\ 
Arithmetic as Logic & 1 & 0.84 & (0.22, 3.12) & \textbf{0.0172*} & 0.23 \\ 
    \bottomrule
 \end{tabular}}
 \label{tab:hypothesis-testing}
 \end{table*}

@@

\begin{table}[!htb]
    \centering
    {\scriptsize
    \caption{Summary of participants' preferences for code snippets \emph{with} and
      \emph{without} atom candidates. The participants were only presented the code snippets, without any indication about whether one was confusing or not. 
      Participants were also allowed to choose Neutral when they thought both sides were equally readable.}
    \begin{tabular}{lrrr}\toprule
      & \multicolumn{3}{c}{\textsc{Preference (\%)}} \\
      \cmidrule(lr){2-4}
         Atom           & \multicolumn{1}{c}{Obfuscated}
                                      &  \multicolumn{1}{c}{Clean}
                                               & \multicolumn{1}{c}{Neutral} \\ \midrule
         Comma Operator                  & 0  & 100    & 0     \\
         Automatic Semicolon Insertion  & 0  & 80     & 0     \\
         Post-Increment                  & 20 & 73.33  & 6.67  \\
         Omitted Curly Braces            & 0  & 100    & 0     \\
         Assignment as Value             & 20 & 60     & 20    \\
         Implicit Predicate              & 20 & 73.33  & 6.67  \\
         Logic as Control Flow           & 20 & 60     & 20    \\
         Conditional Operator                & 60 & 26.67  & 13.3  \\
         Pre-Increment                   & 40 & 46.67  & 13.33 \\ 
         Arithmetic as Logic             & 0  & 93.33  & 6.67  \\ \midrule
         \textsc{overall}                & 18 & 71.33  & 8.64  \\
         \bottomrule
    \end{tabular}
    }
    \label{tab:interview-results1}
\end{table}

@@

The Pre-Increment atom candidate also caused a
conflict in one of the interviewees, who
regarded the clean version as simpler to understand, but would still opt to write
code with the atom. In contrast, %to such opinion,
one of the participants found the version with the atom candidate more elegant, but recognized it was less readable, and was willing to sacrifice elegance for readability. In the repeated measures study, we found a significant difference in favor of the clean version, with a large effect size in its favor. In the latin square study, no difference could be observed in terms of correctness. However, there was a significant difference in terms of the time required to predict the output correctly in favor of the obfuscated version. This highlights how factors such as the experience of the participants and the selection of code snippets can have considerable impact on the results of studies about code readability~\cite{Feitelson:2021:CPC}.
\castor{Should the last sentence above be in the discussion?}
\rb{Agree. We can move it to the discussion section.}
%% \rb{pela discuss\~{a}o anterior, parece-me que alguns
%%   desenvolvedores reconhecem que esses candidatos
%%   a \'{a}tomos introduzem certa dificuldade de compreens\~{a}o;
%%   mas mesmo assim optam por usar a constru\c c\~{a}o correspondente.
%%   Acho que cabe um box aqui com essa discuss\~{a}o sobre isso.}

@@

% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Tue Apr 13 09:34:35 2021
\begin{table}[ht]
  \centering
  {\scriptsize 
\caption{Summary of atom candidate occurrences in our dataset.}
\setlength\tabcolsep{2pt} % default value: 6pt
\begin{tabular}{lrc}%c}
  \toprule
Atom & Projects & Occurr./KLOC \\%& Frequency \\ 
  \midrule
Implicit Predicate & 100\% & 19.89 \\%&  intensively used \\ 
  Conditional Operator & 100\% & 10.16 \\%&  intensively used \\ 
  Omitted Curly Braces & 91.67\% & 6.61 \\%&  intensively used \\ 
  Post Increment & 90.28\% & 5.62 \\%&  intensively used \\ 
  Pre Increment & 83.33\% & 1.04 \\%& commonly used \\ 
  Assignment as Value & 81.94\% & 1.02 \\%& commonly used \\ 
  Logic as Control Flow & 56.94\% & 0.95 \\%& commonly used \\ 
  Automatic Semicolon Insertion & 33.33\% & 0.13 \\%& commonly used \\ 
  Arithmetic as Logic & 23.61\% & 0.02 \\%& rarely used \\ 
  Comma Operator & 15.28\% & 0.03 \\%& rarely used \\
   \bottomrule
\end{tabular}
  }
\label{tab:occurrences-summary}
\end{table}

>>>>

\begin{table}[t!]
\caption{Summary of the correctness analysis.}
\label{tab:diff-correctness-repeated}
\centering{
  \begin{scriptsize}
\begin{tabular}{lrrr} \toprule
  Atom & Obfuscated & Clean & $\Delta$(\%)  \\ \midrule
Type Conversion           &            5 &      27 &                 +440 \\
Change of Literal Encoding &           9 &      36 &                 +300 \\
Comma Operator            &            8 &      29 &                 +262 \\
Object Destructuring      &           15 &      42 &                 +180 \\
Assignment As Value       &           18 &      43 &                 +139 \\
Pre-Increment             &           13 &      28 &                 +115 \\
Post-Increment            &            8 &      17 &                 +112 \\
Array Destructuring       &           15 &      28 &                 +87 \\
Lack of Indentation no Braces     &           30 &      50 &                 +67 \\
Omitted Curly Braces      &           35 &      51 &                 +46 \\
Object Spread             &           21 &      30 &                 +43 \\
Array Spread              &           22 &      31 &                 +41 \\
Automatic Semicolon Insertion &       15 &      21 &                 +40 \\
Infix Operator Precedence &           47 &      53 &                 +13 \\
Arrow Function            &           54 &      58 &                  +7 \\
Implicit Predicate        &           41 &      44 &                  +7 \\
Lack of Indentation With Braces   &           53 &      55 &                  +4 \\
Conditional Operator      &           60 &      62 &                  +3 \\
Constant Variables        &           59 &      61 &                  +3 \\
Dead Unreachable Repeated &           63 &      64 &                  +2 \\
Repurposed Variables      &           23 &      23 &                   0 \\
Arithmetic as Logic       &           52 &      47 &                 -10 \\
Logic as Control Flow     &           33 &      28 &                 -15 \\
Property Access           &           51 &      42 &                 -18 \\
\bottomrule  
\end{tabular}
\end{scriptsize}
}
\end{table}

@@

The ``McNemar test'' column of Table~\ref{tab:repeated:misunderstanding} indicates the p-values for the tests. These p-values are compared against an alpha of 0.0021, after applying Bonferroni correction (0.05/24). One of the atom candidates, Constant Variables, is omitted from the table because, due to the very low number of mistakes, it is not possible to perform the test. The table shows that eight of the 24 analyzed atom candidates can be considered atoms of confusion based on the results of our study, Object Destructuring, Type Conversion, Change of Literal Encoding, Comma Operator, Lack of Indentation No Braces, Assignment as Value, Pre-Increment, and Ommitted Curly Braces. Among these eight, only Object Destructuring is JavaScript-specific. Six of the other atoms have been previously reported for the C language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} and six for Java~\cite{Langhout:2021:ACJ}.
% Lack of Indentation No Braces is not specific to JavaScript and has also been studied by Langhout and Aniche~\cite{Langhout:2021:ACJ}. 
For some candidates that have been previously identified as atoms, there was not a statistically significant difference. This is the case for Repurposed Variables, Logic as Control Flow, Implicit Predicate, and Conditional Operator. We examine this in Section~\ref{sec:discussion}.

@@

\begin{table}[th!]
\caption{Hypotheses Testing (correctness). Asterisks ($^{*}$) indicate a statistically significant difference. Using Bonferroni correction, a p-value is considered statistically significant if it is lower than 0.0021.}
 \centering
 {\scriptsize 
 \begin{tabular}{lrr}
   \toprule
Atom candidate & McNemar test &      Odds Ratio \\
\midrule
Object Destructuring      &   \textbf{$<$ 0.0001*} & $\infty$ \\
Type Conversion           &   \textbf{$<$ 0.0001*} & 12.0 \\
Change of Literal Encoding   &   \textbf{$<$ 0.0001*} & 28.0 \\
Comma Operator            &   \textbf{$<$ 0.0001*} & 11.5 \\
Lack of Indentation No Braces     &   \textbf{$<$ 0.0001*} &  11.0 \\
Assignment As Value       &   \textbf{$<$ 0.0001*} &  9.3 \\
Pre-Increment              &  \textbf{0.0003*} &    16.0 \\
Omitted Curly Braces      &  \textbf{0.0009*} &  6.3 \\
Array Destructuring       &  0.0023 &     7.5 \\
Post-Increment              &  0.0225 &     5.5 \\
Array Spread              &  0.0490 &    3.3 \\
Object Spread             &  0.0636 &     2.8 \\
Property Access           &  0.0636 &     2.8 \\
Infix Operator Precedence &  0.1796 &     2.5 \\
Arrow Function            &  0.2891 &     3.0 \\
Arithmetic As Logic       &  0.3323 &  1.8 \\
Automated Semicolon Insertion  &  0.3915 &  1.4 \\
Logic As Control Flow     &  0.4421 &  1.5 \\
%Constant Variables        &  0.5000 &     0.0 \\
Implicit Predicate        &  0.6900 &  1.3 \\
Lack of Indentation With Braces   &  0.7266 &  1.7 \\
Conditional Operator      &  0.7905 &  1.3 \\
Dead Unreachable Repeated &  1.0000 &     1.5 \\
Repurposed Variables      &   1.0000 &     1.0 \\
\bottomrule
\end{tabular}
}
\label{tab:repeated:misunderstanding}
\end{table}

@@

\begin{table}[htbp]
\caption{Summary of the correctness analysis}
\label{tab:difference-correctness}
\centering{
  {\scriptsize
  \begin{scriptsize}
\begin{tabular}{lrrr} \toprule
  Atom & Obfuscated & Clean & $\Delta$(\%)  \\ \midrule
  Comma Operator                &  28 &  65 & +132   \\ 
  Automatic Semicolon Insertion &  32 &  68 & +112   \\ 
  Post-Increment                &  48 &  64 & +33    \\ 
  Omitted Curly Braces          &  47 &  58 &  +23   \\
  Assignment as Value           &  56 &  68 &  +21   \\ 
  Implicit Predicate            &  58 &  68 &  +17   \\ 
  Logic as Control Flow         &  41 &  48 &  +17   \\ 
  Conditional Operator              &  60 &  66 &  +10   \\ 
  Pre-Increment                 &  50 &  53 &  +6    \\ 
  Arithmetic as Logic           &  64 &  63 &  -2    \\ \bottomrule

@@

\begin{figure}[b!]
\noindent
 \centering
 \includegraphics[width=0.6\columnwidth]{images/wrong-answers-plot-1.pdf}
 \caption{Number of wrong answers of each subject.}
 \label{fig:boxplotcorrectness}
 \end{figure}% \castor{Fiz de tudo para ajeitar a figura porque o texto embaixo deveria ser "Clean versions" e "Confusing versions" mas não sei porque não funcionou. Até mudei a figura. Não sei o que está havendo.}

@@

Finally, we also use a \emph{Binomial Generalized Logistic Regression} analysis to investigate if either \emph{participant education} or \emph{participant experience} impacts correctness. The findings suggest that \emph{participant experience} impacts the results related to correctness (Figure~\ref{fig:correctness-over-experience}). Even though the presence of atoms of confusion reduces the number of correct answers for all \emph{experience groups}, this effect is not uniform. For instance, novice developers (under one year of experience) provide a higher number of wrong answers for the obfuscated version of the code (57.8\%), while developers with more than four years of experience provide more than 70\% of correct answers even when evaluating the obfuscated version of the code snippets. It is also important to note that, independently of the \emph{experience group}, developers tend to provide more than 84\% of correct answers while predicting the outputs for the clean versions of the code. We replicate the \emph{Pearson's Chi-squared test} for each experience group and find that the statistical difference is less significant for those developers with more than ten years of experience. Differently from \emph{participant experience}, the factor \emph{participant education} does not significantly change the correctness of the answers.
\castor{I'd like to have the numbers for the results above. What are the p-values, regression coefficients, etc.?}
\begin{figure}
  \centering
  \includegraphics[scale=0.3]{images/correctness-by-experience}
  \caption{Impact of atoms of confusion on the correctness (over the four participant experience groups)}
  \label{fig:correctness-over-experience}
\end{figure}

@@

\begin{table}[htbp]
\caption{Time in seconds to submit a correct answer}
\centering{
  {\scriptsize
  \begin{scriptsize}
\begin{tabular}{lrrr} \toprule
Atom & Obfuscated  & Clean & $\Delta$(\%) \\ \midrule
Comma Operator & 87.67 & 20.84 & -76.23 \\ 
Automatic Semicolon Insertion & 46.08 & 22.04 & -52.17 \\ 
Post-Increment & 28.70 & 25.67 & -10.56 \\ 
Omitted Curly Braces & 48.85 & 30.00 & -38.58 \\ 
Assignment as Value & 52.47 & 48.95 & -6.71 \\ 
Implicit Predicate & 36.24 & 24.01 & -33.75 \\ 
Logic as Control Flow & 108.94 & 51.07 & -53.12 \\ 
Conditional Operator & 41.80 & 39.34 & -5.90 \\ 
Pre-Increment & 30.71 & 42.45 & 38.19 \\  
Arithmetic as Logic & 28.82 & 37.20 & 29.06 \\ \bottomrule
\end{tabular}
\label{tab:difference-time-taken}
\end{scriptsize}
}}
\end{table}

 % latex table generated in R 4.0.4 by xtable 1.8-4 package
 % Thu Apr 22 07:58:21 2021
 \begin{table*}[ht]
\caption{Hypotheses Testing (misunderstanding and time). Asterisks ($^{*}$) indicate a statistically significant difference.}
 \centering
 {\scriptsize
 \begin{tabular}{lrrr|rr}
   \toprule
Atom  & Chi-square & Odds          & Confidence & Mann-Whitey& Cliff's\\ 
 &  test &Ratio          & Interval &  U test & Delta \\  \midrule
Comma Operator & \textbf{$<$ 0.0001*} & 19.02 & (6.60, 68.22) & \textbf{$<$ 0.0001*} & -0.53 \\ 
Automatic Semicolon Insertion & \textbf{$<$ 0.0001*} & 39.33 & (9.21, 356.62) & 0.0980 & -0.16 \\ 
Post-Increment & \textbf{0.0015*} & 4.83 & (1.73, 15.74) & 0.1201 & 0.15 \\ 
Omitted Curly Braces & 0.0510 & 2.35 & (1.00, 5.77) & 0.9253 & -0.01 \\ 
Assignment as Value & \textbf{0.0035*} & 8.39 & (1.81, 79.12) & 0.8268 & 0.02 \\ 
Implicit Predicate & \textbf{0.0112*} & 6.95 & (1.46, 66.56) & \textbf{0.0029*} & -0.29 \\ 
Logic as Control Flow & 0.2920 & 1.54 & (0.73, 3.28) & \textbf{$<$ 0.0001*} & -0.39 \\ 
Conditional Operator & 0.1590 & 2.73 & (0.74, 12.57) & 0.2407 & -0.12 \\ 
Pre-Increment & 0.7015 & 1.25 & (0.55, 2.85) & \textbf{0.0062*} & 0.27 \\ 
Arithmetic as Logic & 1 & 0.84 & (0.22, 3.12) & \textbf{0.0172*} & 0.23 \\ 
    \bottomrule
 \end{tabular}}
 \label{tab:hypothesis-testing}
 \end{table*}

@@

\begin{table}[!htb]
    \centering
    {\scriptsize
    \caption{Summary of participants' preferences for code snippets \emph{with} and
      \emph{without} atom candidates. The participants were only presented the code snippets, without any indication about whether one was confusing or not. 
      Participants were also allowed to choose Neutral when they thought both sides were equally readable.}\label{tab:interview-results1}
    \begin{tabular}{lrrr}\toprule
      & \multicolumn{3}{c}{\textsc{Preference (\%)}} \\
      \cmidrule(lr){2-4}
         Atom           & \multicolumn{1}{c}{Obfuscated}
                                      &  \multicolumn{1}{c}{Clean}
                                               & \multicolumn{1}{c}{Neutral} \\ \midrule
         Comma Operator                  & 0  & 100    & 0     \\
         Automatic Semicolon Insertion  & 0  & 80     & 0     \\
         Post-Increment                  & 20 & 73.33  & 6.67  \\
         Omitted Curly Braces            & 0  & 100    & 0     \\
         Assignment as Value             & 20 & 60     & 20    \\
         Implicit Predicate              & 20 & 73.33  & 6.67  \\
         Logic as Control Flow           & 20 & 60     & 20    \\
         Conditional Operator                & 60 & 26.67  & 13.3  \\
         Pre-Increment                   & 40 & 46.67  & 13.33 \\ 
         Arithmetic as Logic             & 0  & 93.33  & 6.67  \\ \midrule
         \textsc{overall}                & 18 & 71.33  & 8.64  \\
         \bottomrule
    \end{tabular}
    }

\end{table}

@@

The Pre-Increment atom candidate also caused a
conflict in one of the interviewees, who
regarded the clean version as simpler to understand, but would still opt to write
code with the atom. In contrast, %to such opinion,
one of the participants found the version with the atom candidate more elegant, but recognized it was less readable, and was willing to sacrifice elegance for readability. In the repeated measures study, we found a significant difference in favor of the clean version, with a large effect size in its favor. In the latin square study, no difference could be observed in terms of correctness. However, there was a significant difference in terms of the time required to predict the output correctly in favor of the obfuscated version. 
%% \rb{pela discuss\~{a}o anterior, parece-me que alguns
%%   desenvolvedores reconhecem que esses candidatos
%%   a \'{a}tomos introduzem certa dificuldade de compreens\~{a}o;
%%   mas mesmo assim optam por usar a constru\c c\~{a}o correspondente.
%%   Acho que cabe um box aqui com essa discuss\~{a}o sobre isso.}

@@

% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Tue Apr 13 09:34:35 2021
\begin{table}[ht]
  \centering
  {\scriptsize 
\caption{Summary of atom candidate occurrences in our dataset.}
\setlength\tabcolsep{2pt} % default value: 6pt
\begin{tabular}{lrr}%c}
  \toprule
Atom & Projects & Occurr./KLOC \\%& Frequency \\ 
  \midrule
Implicit Predicate & 100\% & 19.89 \\%&  intensively used \\ 
  Conditional Operator & 100\% & 10.16 \\%&  intensively used \\ 
  Omitted Curly Braces & 91.67\% & 6.61 \\%&  intensively used \\ 
  Post Increment & 90.28\% & 5.62 \\%&  intensively used \\ 
  Pre Increment & 83.33\% & 1.04 \\%& commonly used \\ 
  Assignment as Value & 81.94\% & 1.02 \\%& commonly used \\ 
  Logic as Control Flow & 56.94\% & 0.95 \\%& commonly used \\ 
  Automatic Semicolon Insertion & 33.33\% & 0.13 \\%& commonly used \\ 
  Arithmetic as Logic & 23.61\% & 0.02 \\%& rarely used \\ 
  Comma Operator & 15.28\% & 0.03 \\%& rarely used \\
   \bottomrule
\end{tabular}
  }
\label{tab:occurrences-summary}
\end{table}
